\Large\bf FlexibleSUSY 2.0: Extensions to investigate the phenomenology of SUSY and non-SUSY models

### 2018-04-06 doc/flexiblesusy-2.0.tex
update FS-2.0 paper to version accepted by CPC
with some additional information in the program summary section

\clearpage
\newgeometry{top=2.5cm,left=3cm,right=3cm,bottom=4cm,footskip=3em}
\section*{Program Summary}
\noindent
{\em Program title:} \fs\\[0.5em]
{\em Program obtainable from:} \url{http://flexiblesusy.hepforge.org/}\\[0.5em]
{\em Distribution format:} tar.gz\\[0.5em]
{\em Programming language:} C++, Wolfram/Mathematica, FORTRAN, Bourne shell\\[0.5em]
{\em Computer:} Personal computer\\[0.5em]
{\em Operating system:} Tested on FreeBSD, Linux, Mac OS X, Windows/Cygwin\\[0.5em]
{\em External routines:} \sarah, Boost library, Eigen library, GNU Scientific Library\\[0.5em]
{\em Optional external routines:} BLAS, Himalaya, LAPACK, LoopTools, SQLite, TSIL\\[0.5em]
{\em Typical running time:} 0.02--0.2 seconds per parameter point\\[0.5em]
{\em Nature of problem:}
%
Determining the mass spectrum, mixings and further observables for an arbitrary extension
of the Standard Model, input by the user. The generated code must find
simultaneous solutions to constraints that are specified at two or
more different renormalization scales, which are connected by
renormalization group equations forming a large set of coupled
first-order differential
equations. \\[0.5em]
%
{\em Solution method:}
%
Nested iterative algorithm and numerical
minimization of the Higgs potential.\\[0.5em]
%
{\em Restrictions:}
%
The couplings must remain perturbative at all scales between the
highest and lowest boundary condition.  Tensor-like Lagrangian
parameters of rank 3 are currently not supported.  The automatic
determination of the Standard Model-like gauge and Yukawa couplings is
only supported for models that have the Standard Model gauge group
$SU(3)_C\times SU(2)_L\times U(1)_Y$ as a gauge symmetry group factor.
However, due to the modular nature of the generated code, adapting and
extending it to overcome restrictions in scope is quite straightforward.

>>>>

\clearpage
\newgeometry{top=2.5cm,left=3cm,right=3cm,bottom=4cm,footskip=3em}
\section*{New version program summary}
\noindent
{\em Program title:} \fs\\[0.5em]
{\em Licensing provisions:} GPLv3\\[0.5em]
{\em Program obtainable from:} \url{http://flexiblesusy.hepforge.org/}\\[0.5em]
{\em Programming language:} C++, Wolfram/Mathematica, FORTRAN, Bourne shell\\[0.5em]
{\em Operating system:} Tested on FreeBSD, Linux, Mac OS X, Windows/Cygwin\\[0.5em]
{\em External routines:} \sarah, Boost library, Eigen library, GNU Scientific Library\\[0.5em]
{\em Optional external routines:} BLAS, Himalaya, LAPACK, LoopTools, SQLite, TSIL\\[0.5em]
{\em Journal reference of previous version:} Comput.Phys.Commun.\ 190 (2015) 139-172\\[0.5em]
{\em Does the new version supersede the previous version?:} yes \\[0.5em]
{\em Reasons for the new version:} Program extension including new models, observables and algorithms\\[0.5em]
{\em Summary of revisions:} Extension to non-supersymmetric models
(\fbsm), complex parameters (\fcpv), prediction of $W$ boson mass from
muon decay (\fmw), calculation of anomalous magnetic moment of the
muon (\famu), semi-analytic boundary value problem solver (\fsas),
improved hybrid Higgs mass calculation (\feft).\\[0.5em]
{\em Nature of problem:}
%
Determining the mass spectrum, mixings and further observables for an arbitrary extension
of the Standard Model, input by the user. The generated code must find
simultaneous solutions to constraints that are specified at two or
more different renormalization scales, which are connected by
renormalization group equations forming a large set of coupled
first-order differential
equations. \\[0.5em]
%
{\em Solution method:}
%
Nested iterative algorithm and numerical
minimization of the Higgs potential.\\[0.5em]
%
{\em Restrictions:}
%
The couplings must remain perturbative at all scales between the
highest and lowest boundary condition.  Tensor-like Lagrangian
parameters of rank 3 are currently not supported.  The automatic
determination of the Standard Model-like gauge and Yukawa couplings is
only supported for models that have the Standard Model gauge group
$SU(3)_C\times SU(2)_L\times U(1)_Y$ as a gauge symmetry group factor.
However, due to the modular nature of the generated code, adapting and
extending it to overcome restrictions in scope is quite straightforward.
